Dynamic Prediction with fPCA 

### 2022-11-08 FDAgroup.Rmd
update token

# figure 
bind_rows(df_test %>% 
            select(argvals, subj, Y)%>% 
            rename("y" = "Y") %>% 
            mutate(type = "true", subj = as.factor(subj)), 
          df_test_t0.3 %>% mutate(subj = as.factor(subj))) %>% 
  filter(subj %in% 151:156) %>% 
  ggplot(aes(x = argvals, y = y, col = type))+
  geom_line()+
  facet_wrap(~subj)+
  labs(title = "Prediction with observation up to t=0.3", 
       x = "time", y = "")
```

>>>>

# figure 
bind_rows(df_test %>% 
            select(argvals, subj, Y)%>% 
            rename("y" = "Y") %>% 
            mutate(type = "true", subj = as.factor(subj)), 
          df_test_t0.3 %>% mutate(subj = as.factor(subj))) %>% 
  filter(subj == 152) %>% 
  ggplot(aes(x = argvals, y = y, col = type))+
  geom_line()+
  facet_wrap(~subj)+
  labs(title = "Prediction with observation up to t=0.3", 
       x = "time", y = "")
```
